Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
add an introduction to Section 1.3

We chose to build our library and book on two simple themes which allow many variations: computing powers in a monoid, and Kirby and Paris' hydra battles, formerly user contributions of the Coq system. In the interest of space, we shall present only the second one in this article.

>>>>

We chose to build our library and book on two simple themes which allow many variations: computing powers in a monoid, and Kirby and Paris' hydra battles. In the interest of space, we shall present only the second one in this article.
